\sysfull

### 2017-08-09 paper/evaluation.tex
compiler eval added

We start with evaluating the efficiency of a \sys compiler.

Expected results:
\begin{itemize}
	\item comparison between manual (Chain code) and automatic taskification: in terms of code SLOCs, number of tasks, completion time (Chain), memory use (other metrics required?), show number of LLVM instructions per energy cycle
	\item assessment of correctness (through manual inspection only?).
\end{itemize}

\todo{Provide results and text to this section}{Kiwan}

>>>>

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR Size (Byte)}} & \multicolumn{2}{l|}{{\# Tasks}} & \multicolumn{2}{l|}{{\# Paging Code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp.\\
		\hline\hline
		Bitcount & 22 & 22 & 10 & 15 & 81 & 93 \\
		Cold chain & 3492 & 3242 & 12 & 9 & 92 & 123\\
		Cuckoo & 282 & 288 & 15 & 6 & 90 & 76\\
		RSA & 332 & 250 & 20 & 27 & 130 & 296\\
		AR & 166 & 218 & 11 & 6 & 112 & 333\\
		Sort & 104 & 104 & 4 & 2 & 70 & 23\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated code (Comp.) and hand-written \sys code (Hand).}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of a \sys compiler. Table~\ref{table:compiler_result} shows
the difference in size of protected variable (PVAR), number of tasks, and number of inserted paging call in the code between hand-written \sys code
and compiler-generated \sys code. All three values are better to be small. On average, compiler-generated
code is only worse by 0.3\% in the size of protected variable. Regarding the number of tasks, compiler-generated code
is better by roughly 16\%. The result indicate compiler is selecting boundaries better than programmer manually doing it.
However, compiler should insert paging code conservatively when it {\em may} access protected variable, due to limitation of
pointer alias. Thus, it results in compiler introducing 48\% more paging code than programmer-written code. The resulting run time
difference is summarized in Figure~\ref{}. The performance is worse than programmer-written \sys code
in overall, meaning the programmer should try to write code manually if performance is critical; otherwise compiler can be
used to simplify the programmability.
